|

### 2019-07-16 inst/manuscript/manuscript.Rmd
Update Figure 7

f5_cap <- "\\textbf{Identification of commonly enriched EV proteins across 
           different \\textit{C. albicans} strains.} Heatmap of proteins 
           (n = 396) identified in all four EV samples (venn overlap in Figure 
           \\@ref(fig:figure4)A). Each column represents a 
           \\textit{C. albicans} strain and each row represents a protein. The 
           colours indicate the log\\textsubscript{2}(FC) of the protein for 
           that particular strain; red is EV enriched, blue is EV depleted, and 
           black is EV exclusive. Unsupervised clustering of rows and columns 
           was performed using Gower's formula via the daisy function from the 
           R package \\textit{cluster} [@maechler2019]. Proteins which were 
           exclusive to EVs from all four strains and therefore had no valid 
           log\\textsubscript{2}(FC) values
           were seperated prior to clustering, in the group designated 
           \`\`cluster 8\". Functional enrichment analyses were performed on 
           the heatmap protein clusters using the online tool FungiFun2 
           [@priebe2015]. A selection of significantly enriched GO terms are 
           presented in the table inset. Full lists of enriched GO terms are 
           available in supplemental File S3. Full lists of the proteins 
           in each cluster are available in supplemental File S5.
```

@@

```{r figure7, fig.cap=f7_cap, fig.width=3.5, fig.height=2.8}
f7_cap <- "\\textbf{Twenty-two best potential \\textit{C. albicans} positive EV 
           protein markers.} These proteins are those underlined in Table 
           \\@ref(tab:table1). They are are enriched or exclusive to EVs 
           isolated from all of the \\textit{C. albicans} strains investigated 
           in this study. The proteins fit within the EV biomarker categories 
           1 and 2 from MISEV2018 which includes transmembrane, 
           GPI-anchored, and cytosolic proteins that are EV enriched 
           [@thery2018]."

>>>>

f5_cap <- "\\textbf{Identification of commonly enriched EV proteins across 
           different \\textit{C. albicans} strains.} Heatmap of proteins 
           (n = 396) identified in all four EV samples (venn overlap in Figure 
           \\@ref(fig:figure4)A). Each column represents a 
           \\textit{C. albicans} strain and each row represents a protein. The 
           colours indicate the log\\textsubscript{2}(FC) of the protein for 
           that particular strain; red is EV enriched, blue is EV depleted, and 
           black is EV exclusive. Unsupervised clustering of rows and columns 
           was performed using Gower's formula via the daisy function from the 
           R package \\textit{cluster} [@maechler2019]. Proteins which were 
           exclusive to EVs from all four strains and therefore had no valid 
           log\\textsubscript{2}(FC) values
           were seperated prior to clustering, in the group designated 
           \`\`cluster 8\". Functional enrichment analyses were performed on 
           the heatmap protein clusters using the online tool FungiFun2 
           [@priebe2015]. A selection of significantly enriched GO terms are 
           presented in the table inset. Full lists of enriched GO terms and 
           proteins in each cluster are available in supplemental Files S3 and 
           S5 respectively."
```

@@

```{r figure7, fig.cap=f7_cap, fig.width=4, fig.height=3.6}
f7_cap <- "\\textbf{Twenty-two best potential \\textit{C. albicans} positive EV 
           protein markers.} These proteins are those underlined in Table 
           \\@ref(tab:table1). They are are enriched or exclusive to EVs 
           isolated from all of the \\textit{C. albicans} strains investigated 
           in this study. The proteins fit within the EV biomarker categories 
           1 and 2 from MISEV2018 which includes transmembrane, 
           GPI-anchored, and cytosolic proteins that are EV enriched 
           [@thery2018]."
